### 2019-03-04 README.Rmd
readme improvements

- **data-raw:** Raw data processing.
- **data:** Processed data.
- **R:** Supporting R functions
- **vignettes:** Analysis paper and results.

@@

- Install R (analysis run with `3.5.2`) and Rstudio.

@@

- Load the analysis results by running `vignettes/paper.Rmd`. The complete analysis is not reproducible as the raw data cannot be published, however all interim results are stored in the repository (`data`) and these can be explored.

- Alternatively the complete analysis (along with documentation) can be reconstructed using `make` in the project root directory.

>>>>

- `data-raw`: Raw data processing.
- `data`: Processed data.
- `R`: Supporting R functions.
- `vignettes`: Analysis paper and results.
- `peer-review`: Documentation required for peer review.

@@

- Install R (analysis run with `3.5.2`) and Rstudio (alternatively use Docker as outlined below).

@@

- Load the analysis results by running `vignettes/paper.Rmd`. The complete analysis is not reproducible as the raw data cannot be published, however all interim results are stored in the repository (`data`) and these can be explored. Alternatively the complete analysis (along with documentation) can be reconstructed using `make` in the project root directory.
